---
title: "DS 2020 - Homework #3"
author: "Your name"
format:
    html:
        embed-resources: true
---

```{r}
#| label: setup
#| echo: false
knitr::opts_chunk$set(echo = TRUE)
```

## Chick Weights

The `ChickWeight` data set is part of the base package `datasets`. See `?ChickWeight` for details on the data. For all of the questions use `dplyr` functions whenever possible.

1. **(0.5 pts)** Download the Quarto (qmd) file with these homework instructions to use as a template for your work. Make sure to replace "Your Name" in the YAML with your name. To get full points, show your R code (in a code chunk) and write answers to the questions.

2. **(1 pt)** What variables are part of the dataset?
```{r}

```

> answer


3. **(2 pts)** Get a frequency breakdown of the number of chicks, their average weight, and the standard deviation of the weights in each of the diets at the start of the study.

- extra credit (1 pt): construct a ggplot that shows average weights by diet with an interval (shown as a line) of +- the standard deviation around the averages. (Hint: read this article regarding [ggplot error bars](http://www.sthda.com/english/wiki/ggplot2-error-bars-quick-start-guide-r-software-and-data-visualization))
```{r}

```

> answer


4. **(2 pts)** Each chick should have twelve weight measurements. Use the `dplyr` package to identify how many chicks have a complete set of weight measurements and how many measurements there are on average in the incomplete cases. Extract a subset of the data for all chicks with complete information and name the data set `complete`. (Hint: you might want to use mutate to introduce a helper variable consisting of the number of observations)
```{r}

```

> answer


5. **(2 pts)** In the complete data set introduce a new variable that measures the current weight difference compared to day 0. Name this variable `weightgain`. (Hint: use mutate and `?mutate` to check the parameter `.by`. This parameter can create a temporary `group_by` so that we can do calculation in each subgroup, i.e. weight - Time 0 weight for each chick)
```{r}

```

> answer


6. **(2 pts)** Use `ggplot2` to create side-by-side boxplots of `weightgain` by `Diet` at day 21. Describe the relationship in 2-3 sentences. Change the order of the categories in the Diet variable such that the boxplots are ordered by median `weightgain`.
```{r}

```

> answer


7. **(0.5 pts)** Ensure that your submission is reproducible. We will load your qmd file into Positron and render it. This should match your submitted HTML file.


For the submission: On Canvas, submit your solution in a Quarto (qmd) file and the corresponding HTML file with it, in one zipped folder.

